---
title: "A Very Kaggle Christmas"
output: github_document
---

## Data Wrangling

Let's import the data, remove the variables with no variation or information, and split the data into `train` and `test`.

```{r}
# Load packages.
library(rethinking)
library(tidyverse)
library(tidymodels)
library(rstan)
library(bayesplot)
library(tidybayes)

# Set simulation seed.
set.seed(42)

# Stan options.
options(mc.cores = parallel::detectCores())
rstan_options(auto_write = TRUE)

# Import and mutate data.
data <- read_csv(here::here("Projects", "Data", "data.csv")) %>%
  separate(game_date, into = c("year", "month", "day")) %>%            # Get year, month, and day out of game_date.
  mutate(
    time_remaining = str_c(minutes_remaining, ".", seconds_remaining), # Create a time_remaining variable.
    time_remaining = as.numeric(time_remaining),                       # Make sure it's numeric.
    home = str_detect(matchup, "vs."),                                 # Create a home dummy.
    home = as.numeric(home),                                           # Make sure it's numeric.
    period = as.character(period),                                     # Make sure period is nominal.
    playoffs = as.numeric(playoffs)                                    # Make sure playoffs is numeric.
  ) %>%
  select(
    -c(
      team_id, team_name,                                              # No variation (always Lakers).
      game_event_id, game_id,                                          # Different IDs.
      shot_id,                                                         # Shot ID that is duplicated in shot type variables.
      matchup,                                                         # Variable that we extracted the home game dummy from.
      lat, lon,                                                        # Latitude and longitude (we're using loc_x and loc_y).
      minutes_remaining, seconds_remaining                             # Variables used to create time_remaining.
    )
  )

# Split into training and testing.
train <- data %>% filter(!is.na(shot_made_flag))
test <- data %>% filter(is.na(shot_made_flag)) %>% select(-shot_made_flag)
```

Since our `test` data doesn't have `shot_made_flag` information, we will split our `train` data into a `train_partial` and `valid_partial`. Additionally, we'll use the `recipe` package to expedite data preparation for training and test data.

```{r}
# Split training into training and validation.
train_split <- initial_split(train, prop = 0.8)

# Prepare the data for modeling.
data_recipe <- training(train_split) %>%                       # Create a recipe for data prep.
  recipe(shot_made_flag ~ .) %>%                               # Specify model.
  step_center(loc_x, loc_y, time_remaining, shot_distance) %>% # Center variables.
  step_scale(loc_x, loc_y, time_remaining, shot_distance) %>%  # Scale variables.
  step_dummy(all_nominal()) %>%                                # Create dummies out of all_nominal() variables.
  prep()                                                       # Execute recipe on the training data.

# Extract the prepped training data.
train_partial <- juice(data_recipe)

# Apply the recipe to the validation data and drop rows with NAs.
valid_partial <- data_recipe %>% 
  bake(testing(train_split)) %>% 
  drop_na()

# Apply the recipe to the test data for prediction and replace NAs with 0s.
test_baked <- data_recipe %>% 
  bake(test) %>%
  map_df(replace_na, 0)
```

## Model Fitting and Prediction

Since `shot_made_flag` is binary, we need a non-normal likelihood. The most obvious likelihood is for `shot_made_flag ~ binomial(1, p)` where we can use a logit link function for a linear model `p ~ inv_logit(X * beta)`. Let's start with a flat model.

### Flat Model

```
# Likelihood.
shot_made_flag_n ∼ binomial(1, p)
p_n = inv_logit(X_n * beta), for n = 1:N

# Priors.
beta_i ~ Normal(0, 1), for i = 1:I
```

```{stan model01, output.var="model01", eval=FALSE}
// Index values and observations.
data {
  int<lower = 1> N_train;                  // Number of training data observations.
  int<lower = 1> N_valid;                  // Number of validation data observations.
  int<lower = 1> N_test;                   // Number of test data observations.
  int<lower = 1> I;                        // Number of covariates.
  
  int shot_made_flag[N_train];             // Vector of observations.
  matrix[N_train, I] X_train;              // Matrix of training data covariates.
  matrix[N_valid, I] X_valid;              // Matrix of validation data covariates.
  matrix[N_test, I] X_test;                // Matrix of test data covariates.
}

// Parameters.
parameters {
  vector[I] beta;                         // Vector of coefficients.
}

// Simple regression.
model {
  // LHS of logit link function.
  real p[N_train];
  
  // Priors.
  beta ~ normal(0, 1);

  // Likelihood.
  for (n in 1:N_train) {
    p[n] = inv_logit(X_train[n,] * beta);
  }
  shot_made_flag ~ binomial(1 , p);
}

// Generate predictions using the posterior.
generated quantities {
  real p_valid[N_valid];                 // LHS of logit link function for validation data.
  real y_valid[N_valid];                 // Vector of predicted observations for validation data.
  real p_test[N_test];                   // LHS of logit link function for test data.
  real y_test[N_test];                   // Vector of predicted observations for test data.

  // Generate posterior prediction distribution.
  for (n in 1:N_valid) {
    p_valid[n] = inv_logit(X_valid[n,] * beta);
    y_valid[n] = binomial_rng(1, p_valid[n]);
  }
  for (n in 1:N_test) {
    p_test[n] = inv_logit(X_test[n,] * beta);
    y_test[n] = binomial_rng(1, p_test[n]);
  }
}
```

We include `generated quantities` to compute predictions for the validation and test data at the same time.

Now we can calibrate the model.

```{r eval=FALSE}
# Specify data.
data_list <- list(
  # Covariate index.
  N_train = nrow(train_partial),
  N_valid = nrow(valid_partial),
  N_test = nrow(test_baked),
  I = ncol(train_partial),
  
  # Vector of training data observations.
  shot_made_flag = train_partial$shot_made_flag,
  
  # Matrix of training data covariates.
  X_train = train_partial %>%
    mutate(intercept = 1) %>%
    select(-shot_made_flag),
  
  # Matrix of validation data covariates.
  X_valid = valid_partial %>%
    mutate(intercept = 1) %>%
    select(-shot_made_flag),
  
  # Matrix of testing data covariates.
  X_test = test_baked %>%
    mutate(intercept = 1)
)

# Fit the model and save output.
out03 <- stan(
  file = here::here("Projects", "Code", "model01.stan"),
  data = data_list,
  seed = 42
)
```

How well did model do, based on the validation data?

```{r echo=FALSE}
load(file = here::here("Projects", "Output", "model03-output.RData"))
```

```{r}
# Extract predictions.
y_valid <- rstan::extract(out03)$y_valid
p_test <- rstan::extract(out03)$p_test

# Check with validation.
valid_partial %>% 
  select(shot_made_flag) %>% 
  mutate(y_valid = ifelse(apply(y_valid, 2, mean) > 0.5, 1, 0)) %>% 
  mutate(hit = abs(shot_made_flag - y_valid)) %>% 
  summarize(
    loss = mean(hit),
    hit_rate = 1 - mean(hit)
  )
```

Pretty good. Let's get the submission ready.

```{r eval=FALSE}
# Prepare submission.
read_csv(here::here("Projects", "Data", "sample_submission.csv")) %>% 
  select(shot_id) %>% 
  mutate(shot_made_flag = apply(p_test, 2, mean)) %>% 
  write_csv(here::here("Projects", "Output", "submission.csv"))
```

We get a `0.611` loss on the test data, better than the deep learning model but not as good as boosting.


